Our Title

### 2015-05-01 draft.tex
Added in Julie's draft Goals section.

    ISIL is an adherent to the Salafi movement of Sunni Islam \cite{Bradley2015}, itself a very orthodox school of thought among Muslim theology.  As such, it promotes a reform of Islam back to its roots with Muhammad, and an extremely literal interpretation of the Quran and Hadith \cite{Hassan2015}. Many modern Jihadist groups are devout adherents to Salafi Islam. Salafists  advocate Jihad and the conquest of all peoples (specifically the West) by forcible conversion, execution, or subjugation through conquest, driving towards a global Caliphate. ISIL shares these beliefs with other modern Islamic Jihadist groups, including the Muslim Brotherhood and al-Qaeda, due to its support of religious violence and terrorism \cite{schmidt2004great,gabriel2008they,Hassan2015,Moussalli2009}.

    One significant difference between ISIL and other mainstream Sunni Muslims is that ISIL violently condemns all Muslims who disagree with its interpretations as infidels and apostates, promoting  sectarian violence for deviating from the \enquote{pure Islam} that ISIL follows. They also advocate this same violence against journalists, civilians, relief workers, and any other individuals or groups whom ISIL believes are supporting any infidel \cite{Wood2015,Hassan2015,AustralianNationalSecurityAttorney-GeneralsDepartment2014}. It is these extreme levels of sectarian violence that has earned ISIL condemnation from mainstream Sunni and Shia clerics, as ISIL's public show of fundamentalist Islam gives Islam a violent appearance in the eyes of the global community \cite{Mandhai2014}.

@@

waiting on Julie.

@@

>>>>

    ISIL is an adherent to the Salafi movement of Sunni Islam \cite{Bradley2015}, itself a very orthodox school of thought among Muslim theology.  As such, it promotes a reform of Islam back to its roots with Muhammad, and an extremely literal interpretation of the Quran and Hadith \cite{Hassan2015}. Many modern Jihadist groups are devout adherents to Salafi Islam, which requires that all true believers live the tenets of the Quran to the letter. Salafists  advocate Jihad and the conquest of all peoples (specifically the West) by forcible conversion, execution, or subjugation through conquest, driving towards a global Caliphate. ISIL shares these beliefs with other modern Islamic Jihadist groups, including the Muslim Brotherhood and al-Qaeda, due to its support of religious violence and terrorism \cite{schmidt2004great,gabriel2008they,Hassan2015,Moussalli2009}.

    One significant difference between ISIL and other mainstream Sunni Muslims is that ISIL violently condemns all Muslims who disagree with its interpretations as infidels and apostates, promoting  sectarian violence for deviating from the \enquote{pure Islam} that ISIL follows. They also advocate this same violence against journalists, civilians, relief workers, and any other individuals or groups whom ISIL believes are supporting any infidel \cite{Wood2015,Hassan2015,AustralianNationalSecurityAttorney-GeneralsDepartment2014}. Many of the atrocities that have so shocked the world - beheadings, burnings, forced marriages - result from this commitment of ISIL to live the tenets of the Quran to the letter. It is these extreme levels of  violence (sectarian and otherwise) that has earned ISIL condemnation from mainstream Sunni and Shia clerics, as ISIL's public show of fundamentalist Islam gives Islam a violent appearance in the eyes of the global community \cite{Mandhai2014}.

@@

\subsection{????????  Needs expansion  and references   ????????????}

Since ISIL began to seize power and land in Iraq and Syria, many of studied what exactly drives the organization. Perhaps the most complete discussion of the group's motivation comes from Graeme Woods’ article \enquote{What ISIL Really Wants,} which appeared in the March 2015 issue of The Atlantic \cite{Wood2015}. In assessing ISIL and its goals, it is first necessary to recognize its differences with other militant Islamic terrorist organizations.

The strict brand of Salafism which ISIL espouses has also led to another important distinction between ISIL and other terrorist organizations: the establishment of a Caliphate, with Abu Bakr al-Baghdadi as Caliph. A Caliphate is a homeland for Muslims, and ISIL believes that its establishment is necessary for it to truly follow the tenets of Islam. While other terrorist organizations were content to live amongst the people in various countries, ISIL has seized territory and established a government. In their orthodox and literal interpretation of Islam, the division of the Middle East into its current countries was driven by Western countries, and is therefore fundamentally illegitimate and cannot be tolerated.

The taking and protection of territory by ISIL is one of its core goals. Under the tenets of Salafism, a Caliphate cannot exist without land, and so maintaining a geographic foothold is fundamental to the existence of ISIL. Without it, their caliphate will cease to exist.

Much discussion has surrounded the flow of foreign fighters into ISIL controlled territory. Again, this is rooted in the groups’ religious beliefs. According to Salafism, once a caliphate is established, all true believers must move to it, unless completely unable to do so.

ISIL poses a more direct threat to its neighbors than to the US homeland. While many foreigners with Western passports have pledged allegiance to ISIL, they often do so with no intent to return, as illustrated by the common burning of passports once individuals reach ISIL territory. Additionally, ISIL must continue to expand, taking territory from “illegitimate” governments, in order to maintain its own legitimacy as a Caliphate.

@@

Missing
